APPM report - Draft

### 2022-12-21 paper_version/main.tex
add tilde before \ref{}

% \mycomment{Roman: more info from a physical point of view?} R.H. 19.12. Extended paragraph
The starting point for this work was the desire to numerically simulate the formation and
evolution of electric arcs at atmospheric pressures. Following common practise, we rely on
a mathematical description by means of a hydrodynamic multi-species plasma model, which
boils down to an extended Maxwell-Euler system. The arc phenomenon covers a wide range of
plasma regimes and, thus, the design goal was a numerical model capable of dealing
with all of them seamlessly and simultaneously. Thus in this work, as in
\cite{degond_2012}, the focus is on \emph{asymptotic-preserving} (AP) discretization in
the quasi-neutral limit $\lambda \rightarrow 0$, where $\lambda$ is the rescaled Debye
length, see Section \ref{sec:rescaling} for the underlying scaling arguments and
\cite{degond_2012,degond_2017} for a discussion of the importance of the AP property of
numerical plasma models.

@@

We stay close to \cite{degond_2012} in terms of discretization in time employing
semi-implicit time-stepping. We also base our considerations on the model geometry shown
in Fig. \ref{fig:domain_geometry}. We would like to remark that the mesh-based numerical
scheme proposed in this paper can in principle be adapted to geometric situations much
more general than that of Fig. \ref{fig:domain_geometry}. However, one may encounter
subtle problems in defining proper dual meshes as we need it in Section
\ref{sec:mesh-duality}. Thus, for the sake of simplicity of presentation we forgo
geometric generality.

The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed
problem, that is, the limiting PDE system changes its type\footnote{The type of the
  Maxwell-Euler system switches from hyperbolic to mixed for $\lambda_{D}\to 0$}. This
poses a challenge for simulations in settings encompassing different regimes. We remind
that singularly perturbed problems occur in many physical models, e.g., in the case of
vanishing viscosity in the Navier-Stokes equations \cite{Kato_1984}, the
zero-relaxation-limit of kinetic equations \cite{jin_2010}, and the zero-Mach-number limit
of compressible flows \cite{degond_2007, haack_2010}. Throughout, it is essential that
numerical schemes remain valid even if crucial model parameters approach the limit. These
schemes are then said to be \emph{asymptotic-preserving} (AP): Let us assume that we
discretize a parameter($\lambda$)-dependent model $P^\lambda$, which converges to a limit
$P^0$ as $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some
discretization parameter, e.g., the mesh size. The AP property amounts to uniform
convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. Readers are
referred to the illustration by a commuting diagram in \cite[][Fig. 1]{jin_2010} and, more
generally, to the comprehensive reviews \cite{jin_2010, degond_2017} for more details
about AP schemes.

The content of this paper is organized as follows: In Section \ref{sec:plasma-model}, we
give a full description of the underlying equations of the Maxwell-Euler system and its
rescaling procedure. Meanwhile, the boundary conditions in our setting is elaborated. A
reformulation of Maxwell's equations in the non-conducting region is presented. Section
\ref{sec:spatial_discretization} is devoted to the spatial discretization. The concept of
primal-dual meshes is introduced based on which FIT and FVM are utilized. We discuss the
full AP discretization in Section \ref{sec:full-discretization} and do numerical
experiments in Section \ref{sec:numerical_experiment}.

@@

We consider a simply-connected domain $\Omega$ comprising two sub-domains $\Omega_P$
(\textbf{p}lasma domain) and $\Omega_N$ (\textbf{n}on-conducting domain). They represent
regions of space occupied by plasma and a non-conducting linear dielectric medium
(e.g. glass) respectively. We use the notation
$\Gamma_C := \partial\Omega \cap \partial\Omega_P$ to denote the contact boundary, and
$\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary which is an
``artificial'' cut-off boundary. The interface between the two domains is denoted by
$\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$. A geometric arrangement corresponding
to this setting is sketched in Fig. \ref{fig:domain_sketch} and is the one used in
\cite[][Ch. 1, Sec. 4]{fuchs_2021}. This situation is simple, but highly relevant. It
covers fundamental experimental set-ups, for example, those studying wall-stabilized
electric arcs \cite{GGF05}, but is also adequate for a range of industrial plasmas, for
instance, for those occurring in high-voltage circuit breakers \cite{SEE15,MGU20}.

@@

No plasma fills the non-conducting domain $\Omega_N$ (see Fig. \ref{fig:domain_sketch}),
and, consequently, the Maxwell system in $\Omega_N$ reduces to 
\begin{subequations}
  \label{eq:mxon}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins}.
\end{align}
\end{subequations}
In a non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$
is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are
redundant as long as they are satisfied at initial time. Nonetheless, as the system
approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for the
$\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate. Schemes based on this set
of PDEs would become unstable as $\lambda \rightarrow 0$. The vanishing divergence
constraint would evaporate as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold
numerically when $\lambda^2$ becomes extremely small.

@@

Supplemented with the boundary condition $\psi = 0$ on $\partial\Omega_N$, one can check
that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to
the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that
$\psi = 0$ in $\Omega_N$. This is done by taking the divergence of
(\ref{equ:ampere_ins_reform}), which results in $\Delta\psi = 0$ and the zero Dirichlet
boundary condition gives vanishing $\psi$. The importance of this reformulation will
become clear through numerical experiments, see Section \ref{sec:numerical_experiment}.

@@

In 2D we construct the pair of meshes based on the Delaunay-Voronoi approach: we start with a
Delaunay triangulation $\mathcal{M}$ of the domain and construct $\Tilde{\mathcal{M}}$ by
connecting \emph{circumcenters} of any two adjacent triangles, see Fig. \ref{fig:2d-mesh}.
In three dimensions, the meshes are constructed by extruding the 2D meshes vertically
along one axis in a staggered manner \cite[][Sec. 3.1]{Marrone_2001}. See an example in
Fig. \ref{fig:2d-extrusion}. In this way, the meshes are composed of prisms. This
particular choice is compatible with the cylindrical geometric setting that we are in, see
Fig. \ref{fig:domain_sketch}. For a general setting, one can directly decompose the domain
into tetrahedrons and constructs the Voronoi grid, but the procedure is more
complicated. The meshes for the cylindrical domain are displayed in
Fig. \ref{fig:primal_dual_meshes}.

The geometric orthogonality between $L \leftrightarrow \Tilde{A}$ and
$A \leftrightarrow \Tilde{L}$ is satisfied and will be a crucial property for
approximating the material laws on the discrete level (which is the so-called discrete
Hodge operator \cite{hip_1999, bossavit1999}), as will be shown in Section \ref{sec:fit}.

@@

Each geometric entity in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an
\emph{internal orientation}\footnote{This notion should not be confused with \emph{inner
    orientation}, which has a slightly different definition, see
  \cite[][Sec. 3.1]{tonti_2002}.}. The notion is illustrated in
Fig. \ref{fig:orientation}. For the entities of the dual mesh $\Tilde{\mathcal{M}}$, we
set their internal orientations to be aligned with their corresponding primal entities
according to the bijective pairings, i.e. edges penetrate faces.

Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim entity $f$ with respect to a (k+1)-dim entity $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rules shown in Fig. \ref{fig:orientation}.

This information can be described by matrices with entries in $\{0,-1,+1\}$, called \emph{incidence matrices}. To describe the primal face-to-edge relation, for instance, a sparse matrix $\mathbb{C} \in \mathbb{R}^{N_A \times N_L}$ is assembled whose $(i,j)$-entry is assigned $+1$ if the internal orientation of edge $L_j$ and its induced orientation with respect to face $A_i$ coincides; it is assigned $-1$ if two orientations are opposite; and assigned $0$ if $L_j$ is not a subset of the boundary of $A_i$. We will see later that $\mathbb{C}$ functions as a discrete version of the rotation operator. The other incidence matrices are constructed in the same manner, see Tab. \ref{tab:incidence_mat} for a summary. Given the relationship of orientations of $\mathcal{M}$ and $\Tilde{\mathcal{M}}$, we can derive the relations listed in Tab. \ref{tab:incidence_relation}.

@@

Note that the auxiliary edges might not be straight and the auxiliary faces might not be
flat as is shown in Fig. \ref{fig:illustraion_dual_boundary}, which necessitates a
versatile data structure to include such situations. In the following, the auxiliary
entities would be treated as dual entities, which limits the validity of the relations in
Tab. \ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$. For a more
systematic illustration that considers the boundary dual entities, see
\cite[][Sec. 5]{hip_1999}.

@@

A pair of primal and dual meshes for the geometry in Fig. \ref{fig:domain_sketch} is displayed in Fig. \ref{fig:primal_dual_meshes}.

@@

The electromagnetic boundary $\partial\Omega = \Gamma_C\cup \Gamma_I$ is resolved by the
primal mesh $\mathcal{M}$. As is mentioned in Section \ref{sec:BC}, the zero-magnetic-flux
boundary condition $\mathbf{B}\cdot \mathbf{n}$ is equivalent to
$(\nabla\times\mathbf{E}) \cdot \mathbf{n} = 0$, which paves the way for a surface scalar
potential $\varphi:\partial\Omega\to\mathbb{R}$ such that the tangential component
$\mathbf{E}_t$ of the $\mathbf{E}$-field is equal to $\nabla_\Gamma\varphi$. This remains
true on the discrete level. We associate with each primal vertex $P_k \in \partial\Omega$
a scalar value $\varphi_k$. Therefore, the boundary conditions (see Section \ref{sec:BC})
are discretized in the following way:
\begin{center}
    \vspace{-0.5cm}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
    \mathbf{D} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \mathbf{B} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I, \\
    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm,
    \end{align*}
    \end{minipage}
    \begin{minipage}{0.1\textwidth}
    \centering
    \begin{tikzpicture}
    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
    \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \centering
        \begin{subequations}
            \begin{align}
            d_k = 0,\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I,\label{equ:bc_3} \\
            e_k = (\mathbb{GX}_\varphi\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \label{equ:bc_2}\\
            \varphi_k = \varphi^\pm(t), \ \ &\forall k : P_k \subset \Gamma_C^\pm, \label{equ:bc_1}
            \end{align}
        \end{subequations}
    \end{minipage}
\end{center}
where $\mathbb{X}_\varphi \in \mathbb{R}^{N_P \times N_P^\partial}$ extends $\bm{\varphi}$
to all the primal verices by zero. Obviously, the surface gradient $\nabla_\Gamma$ is
represented by $\mathbb{GX}_\varphi$.

@@

In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell
system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier. On
the semi-discrete level, the equations to be solved in $\Omega_N$ are
\begin{center}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
        \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\ 
        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla \psi$} &= 0, \\
        \nabla \cdot \mathbf{D} &= 0. 
    \end{align*}
    \end{minipage}
    \begin{minipage}{0.1\textwidth}
    \centering
    \begin{tikzpicture}
    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
    \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \begin{subequations}
        \begin{align}
            [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0}]_k,\ \ \forall k:A_k \subset \Omega_N,\\
            [\lambda^2\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbb{X}_\psi \bm{\psi}$}&= \mathbf{0}]_k, \ \ \forall k: \Tilde{A}_k \subset \Omega_N \label{equ:discrete_ampere_ins}\\
            [\Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{0}]_k,\ \ \forall k:\Tilde{V}_k \subset \Omega_N \label{equ:discrete_zero_div}, 
        \end{align} 
    \end{subequations}
    \end{minipage}
\end{center}
where $\bm{\psi} := \{\psi_k\}_{k=1}^{N_P^N}$ denotes unknowns assigned to each primal
vertex in $\Omega_N$. The matrix $\mathbb{X}_\psi \in \mathbb{R}^{N_P \times N_P^{N}}$
extends $\bm{\psi}$ by zero to all the primal vertices. This way the zero Dirichlet
boundary condition is incorporated. We need the diagonal matrix
$(\mathbb{H})_{k,k} = {|\Tilde{A}_k|}/{|L_k|}$ to transform primal edge integrals to dual
face fluxes since the discrete Amp\`{e}re's law (\ref{equ:discrete_ampere_ins}) is defined
on dual faces on $\Omega_N$.

@@

Since the electromagnetic fields are represented by integrals on edges and faces, we need
to reconstruct their vector components for the computation of Lorentz force (and Joule
heating) inside each dual cell. The task involves two aspects:
\begin{itemize}
    \item[-] given the fluxes at the faces of a cell, reconstruct the vector field inside the cell;
    \item[-] given the integrals along the edges of a cell, reconstruct the vector field inside the cell. 
\end{itemize}
We adopt the principle of least square fitting and reconstruct a \emph{constant} vector
field inside each cell. For a cell $\Tilde{V}$ with $N_A$ faces with areas
$\{A_k\}_{k=1}^{N_A}$, normal vectors $\{\mathbf{n}_k\}_{k=1}^{N_A}$ and fluxes
$\{f_k\}_{k=1}^{N_A}$, a constant vector field $\mathbf{v}$ satisfying
\begin{equation*}
    \mathbf{v} = \argmin_{\mathbf{w}\in \mathbb{R}^3} \sum_{k=1}^{N_A}(A_k\mathbf{w} \cdot \mathbf{n}_k - f_k)^2.   
\end{equation*} can be computed through
\begin{equation*}
    \mathbf{v} = (\mathbb{K}^T\mathbb{K})^{-1}\mathbb{K}^T\mathbf{f},
\end{equation*}
where
\begin{equation*}
    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_{N_A}\mathbf{n}_{N_A}]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_{N_A}]^T,
\end{equation*}
and each vector in $\mathbb{R}^3$ is treated as a column vector. The construction based on
the integral quantities on edges can be done similarly. Assembling the local constructions
for each dual cell, the global construction can be written as
\begin{equation}
    \mathbf{E} = \Tilde{\mathbb{R}}_E\mathbf{d}\;,
    \quad
    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b},
    \label{equ:reconstruction}
\end{equation}
where $\mathbf{d}, \mathbf{b}$ are defined in Tab. \ref{tab:def_size_var};
$\mathbf{E} := \{\mathbf{E}_k\}_{k=1}^{N_{\Tilde{V}}}$ and
$\mathbf{B} := \{\mathbf{B}_k\}_{k=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$
matrices containing the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each
$\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.

@@

3D FIT/DEC-FVM framework presented in Section \ref{sec:spatial_discretization} and the

>>>>

% \mycomment{Roman: more info from a physical point of view?} R.H. 19.12. Extended paragraph
The starting point for this work was the desire to numerically simulate the formation and
evolution of electric arcs at atmospheric pressures. Following common practise, we rely on
a mathematical description by means of a hydrodynamic multi-species plasma model, which
boils down to an extended Maxwell-Euler system. The arc phenomenon covers a wide range of
plasma regimes and, thus, the design goal was a numerical model capable of dealing
with all of them seamlessly and simultaneously. Thus in this work, as in
\cite{degond_2012}, the focus is on \emph{asymptotic-preserving} (AP) discretization in
the quasi-neutral limit $\lambda \rightarrow 0$, where $\lambda$ is the rescaled Debye
length, see Section~\ref{sec:rescaling} for the underlying scaling arguments and
\cite{degond_2012,degond_2017} for a discussion of the importance of the AP property of
numerical plasma models.

@@

We stay close to \cite{degond_2012} in terms of discretization in time employing
semi-implicit time-stepping. We also base our considerations on the model geometry shown
in Fig.~\ref{fig:domain_geometry}. We would like to remark that the mesh-based numerical
scheme proposed in this paper can in principle be adapted to geometric situations much
more general than that of Fig.~\ref{fig:domain_geometry}. However, one may encounter
subtle problems in defining proper dual meshes as we need it in Section
\ref{sec:mesh-duality}. Thus, for the sake of simplicity of presentation we forgo
geometric generality.

The quasi-neutral limit of the Maxwell-Euler system leads to a singularly perturbed
problem, that is, the limiting PDE system changes its type\footnote{The type of the
  Maxwell-Euler system switches from hyperbolic to mixed for $\lambda_{D}\to 0$}. This
poses a challenge for simulations in settings encompassing different regimes. We remind
that singularly perturbed problems occur in many physical models, e.g., in the case of
vanishing viscosity in the Navier-Stokes equations \cite{Kato_1984}, the
zero-relaxation-limit of kinetic equations \cite{jin_2010}, and the zero-Mach-number limit
of compressible flows \cite{degond_2007, haack_2010}. Throughout, it is essential that
numerical schemes remain valid even if crucial model parameters approach the limit. These
schemes are then said to be \emph{asymptotic-preserving} (AP): Let us assume that we
discretize a parameter($\lambda$)-dependent model $P^\lambda$, which converges to a limit
$P^0$ as $\lambda \rightarrow 0$, by the scheme $P^\lambda_h$ where $h$ denotes some
discretization parameter, e.g., the mesh size. The AP property amounts to uniform
convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. Readers are
referred to the illustration by a commuting diagram in \cite[][Fig.~1]{jin_2010} and, more
generally, to the comprehensive reviews \cite{jin_2010, degond_2017} for more details
about AP schemes.

The content of this paper is organized as follows: In Section~\ref{sec:plasma-model}, we
give a full description of the underlying equations of the Maxwell-Euler system and its
rescaling procedure. Meanwhile, the boundary conditions in our setting is elaborated. A
reformulation of Maxwell's equations in the non-conducting region is presented. Section
\ref{sec:spatial_discretization} is devoted to the spatial discretization. The concept of
primal-dual meshes is introduced based on which FIT and FVM are utilized. We discuss the
full AP discretization in Section~\ref{sec:full-discretization} and do numerical
experiments in Section~\ref{sec:numerical_experiment}.

@@

We consider a simply-connected domain $\Omega$ comprising two sub-domains $\Omega_P$
(\textbf{p}lasma domain) and $\Omega_N$ (\textbf{n}on-conducting domain). They represent
regions of space occupied by plasma and a non-conducting linear dielectric medium
(e.g. glass) respectively. We use the notation
$\Gamma_C := \partial\Omega \cap \partial\Omega_P$ to denote the contact boundary, and
$\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary which is an
``artificial'' cut-off boundary. The interface between the two domains is denoted by
$\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$. A geometric arrangement corresponding
to this setting is sketched in Fig.~\ref{fig:domain_sketch} and is the one used in
\cite[][Ch. 1, Sec. 4]{fuchs_2021}. This situation is simple, but highly relevant. It
covers fundamental experimental set-ups, for example, those studying wall-stabilized
electric arcs \cite{GGF05}, but is also adequate for a range of industrial plasmas, for
instance, for those occurring in high-voltage circuit breakers \cite{SEE15,MGU20}.

@@

No plasma fills the non-conducting domain $\Omega_N$ (see Fig.~\ref{fig:domain_sketch}),
and, consequently, the Maxwell system in $\Omega_N$ reduces to 
\begin{subequations}
  \label{eq:mxon}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins}.
\end{align}
\end{subequations}
In a non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$
is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are
redundant as long as they are satisfied at initial time. Nonetheless, as the system
approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for the
$\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate. Schemes based on this set
of PDEs would become unstable as $\lambda \rightarrow 0$. The vanishing divergence
constraint would evaporate as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold
numerically when $\lambda^2$ becomes extremely small.

@@

Supplemented with the boundary condition $\psi = 0$ on $\partial\Omega_N$, one can check
that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to
the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that
$\psi = 0$ in $\Omega_N$. This is done by taking the divergence of
(\ref{equ:ampere_ins_reform}), which results in $\Delta\psi = 0$ and the zero Dirichlet
boundary condition gives vanishing $\psi$. The importance of this reformulation will
become clear through numerical experiments, see Section~\ref{sec:numerical_experiment}.

@@

In 2D we construct the pair of meshes based on the Delaunay-Voronoi approach: we start with a
Delaunay triangulation $\mathcal{M}$ of the domain and construct $\Tilde{\mathcal{M}}$ by
connecting \emph{circumcenters} of any two adjacent triangles, see Fig.~\ref{fig:2d-mesh}.
In three dimensions, the meshes are constructed by extruding the 2D meshes vertically
along one axis in a staggered manner \cite[][Sec. 3.1]{Marrone_2001}. See an example in
Fig.~\ref{fig:2d-extrusion}. In this way, the meshes are composed of prisms. This
particular choice is compatible with the cylindrical geometric setting that we are in, see
Fig.~\ref{fig:domain_sketch}. For a general setting, one can directly decompose the domain
into tetrahedrons and constructs the Voronoi grid, but the procedure is more
complicated. The meshes for the cylindrical domain are displayed in
Fig.~\ref{fig:primal_dual_meshes}.

The geometric orthogonality between $L \leftrightarrow \Tilde{A}$ and
$A \leftrightarrow \Tilde{L}$ is satisfied and will be a crucial property for
approximating the material laws on the discrete level (which is the so-called discrete
Hodge operator \cite{hip_1999, bossavit1999}), as will be shown in Section~\ref{sec:fit}.

@@

Each geometric entity in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an
\emph{internal orientation}\footnote{This notion should not be confused with \emph{inner
    orientation}, which has a slightly different definition, see
  \cite[][Sec. 3.1]{tonti_2002}.}. The notion is illustrated in
Fig.~\ref{fig:orientation}. For the entities of the dual mesh $\Tilde{\mathcal{M}}$, we
set their internal orientations to be aligned with their corresponding primal entities
according to the bijective pairings, i.e. edges penetrate faces.

Another orientation attribute, \emph{induced orientation}, is defined as follows: an induced orientation of a k-dim entity $f$ with respect to a (k+1)-dim entity $f'$, satisfying $f \subset \partial f' $, is determined by the internal orientation of $f'$ according to the rules shown in Fig.~\ref{fig:orientation}.

This information can be described by matrices with entries in $\{0,-1,+1\}$, called \emph{incidence matrices}. To describe the primal face-to-edge relation, for instance, a sparse matrix $\mathbb{C} \in \mathbb{R}^{N_A \times N_L}$ is assembled whose $(i,j)$-entry is assigned $+1$ if the internal orientation of edge $L_j$ and its induced orientation with respect to face $A_i$ coincides; it is assigned $-1$ if two orientations are opposite; and assigned $0$ if $L_j$ is not a subset of the boundary of $A_i$. We will see later that $\mathbb{C}$ functions as a discrete version of the rotation operator. The other incidence matrices are constructed in the same manner, see Tab.~\ref{tab:incidence_mat} for a summary. Given the relationship of orientations of $\mathcal{M}$ and $\Tilde{\mathcal{M}}$, we can derive the relations listed in Tab.~\ref{tab:incidence_relation}.

@@

Note that the auxiliary edges might not be straight and the auxiliary faces might not be
flat as is shown in Fig.~\ref{fig:illustraion_dual_boundary}, which necessitates a
versatile data structure to include such situations. In the following, the auxiliary
entities would be treated as dual entities, which limits the validity of the relations in
Tab.~\ref{tab:incidence_relation} to interior part of $\Tilde{\mathcal{M}}$. For a more
systematic illustration that considers the boundary dual entities, see
\cite[][Sec. 5]{hip_1999}.

@@

A pair of primal and dual meshes for the geometry in Fig.~\ref{fig:domain_sketch} is displayed in Fig.~\ref{fig:primal_dual_meshes}.

@@

The electromagnetic boundary $\partial\Omega = \Gamma_C\cup \Gamma_I$ is resolved by the
primal mesh $\mathcal{M}$. As is mentioned in Section~\ref{sec:BC}, the zero-magnetic-flux
boundary condition $\mathbf{B}\cdot \mathbf{n}$ is equivalent to
$(\nabla\times\mathbf{E}) \cdot \mathbf{n} = 0$, which paves the way for a surface scalar
potential $\varphi:\partial\Omega\to\mathbb{R}$ such that the tangential component
$\mathbf{E}_t$ of the $\mathbf{E}$-field is equal to $\nabla_\Gamma\varphi$. This remains
true on the discrete level. We associate with each primal vertex $P_k \in \partial\Omega$
a scalar value $\varphi_k$. Therefore, the boundary conditions (see Section~\ref{sec:BC})
are discretized in the following way:
\begin{center}
    \vspace{-0.5cm}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
    \mathbf{D} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \mathbf{B} \cdot \mathbf{n} = 0\ \  &\text{on} \ \  \Gamma_I, \\
    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm,
    \end{align*}
    \end{minipage}
    \begin{minipage}{0.1\textwidth}
    \centering
    \begin{tikzpicture}
    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
    \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \centering
        \begin{subequations}
            \begin{align}
            d_k = 0,\ \ &\forall k : \Tilde{A}_k \subset \Gamma_I,\label{equ:bc_3} \\
            e_k = (\mathbb{GX}_\varphi\bm{\varphi})_k,\ \ &\forall k : L_k \subset \partial\Omega, \label{equ:bc_2}\\
            \varphi_k = \varphi^\pm(t), \ \ &\forall k : P_k \subset \Gamma_C^\pm, \label{equ:bc_1}
            \end{align}
        \end{subequations}
    \end{minipage}
\end{center}
where $\mathbb{X}_\varphi \in \mathbb{R}^{N_P \times N_P^\partial}$ extends $\bm{\varphi}$
to all the primal verices by zero. Obviously, the surface gradient $\nabla_\Gamma$ is
represented by $\mathbb{GX}_\varphi$.

@@

In Section~\ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell
system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier. On
the semi-discrete level, the equations to be solved in $\Omega_N$ are
\begin{center}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
        \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\ 
        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} + \colorbox{orange!20}{$\nabla \psi$} &= 0, \\
        \nabla \cdot \mathbf{D} &= 0. 
    \end{align*}
    \end{minipage}
    \begin{minipage}{0.1\textwidth}
    \centering
    \begin{tikzpicture}
    \draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
    \end{tikzpicture}
    \end{minipage}
    \begin{minipage}{0.5\textwidth}
        \begin{subequations}
        \begin{align}
            [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0}]_k,\ \ \forall k:A_k \subset \Omega_N,\\
            [\lambda^2\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \colorbox{orange!20}{$\mathbb{H} \mathbb{G} \mathbb{X}_\psi \bm{\psi}$}&= \mathbf{0}]_k, \ \ \forall k: \Tilde{A}_k \subset \Omega_N \label{equ:discrete_ampere_ins}\\
            [\Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{0}]_k,\ \ \forall k:\Tilde{V}_k \subset \Omega_N \label{equ:discrete_zero_div}, 
        \end{align} 
    \end{subequations}
    \end{minipage}
\end{center}
where $\bm{\psi} := \{\psi_k\}_{k=1}^{N_P^N}$ denotes unknowns assigned to each primal
vertex in $\Omega_N$. The matrix $\mathbb{X}_\psi \in \mathbb{R}^{N_P \times N_P^{N}}$
extends $\bm{\psi}$ by zero to all the primal vertices. This way the zero Dirichlet
boundary condition is incorporated. We need the diagonal matrix
$(\mathbb{H})_{k,k} = {|\Tilde{A}_k|}/{|L_k|}$ to transform primal edge integrals to dual
face fluxes since the discrete Amp\`{e}re's law (\ref{equ:discrete_ampere_ins}) is defined
on dual faces on $\Omega_N$.

@@

Since the electromagnetic fields are represented by integrals on edges and faces, we need
to reconstruct their vector components for the computation of Lorentz force (and Joule
heating) inside each dual cell. The task involves two aspects:
\begin{itemize}
    \item[-] given the fluxes at the faces of a cell, reconstruct the vector field inside the cell;
    \item[-] given the integrals along the edges of a cell, reconstruct the vector field inside the cell. 
\end{itemize}
We adopt the principle of least square fitting and reconstruct a \emph{constant} vector
field inside each cell. For a cell $\Tilde{V}$ with $N_A$ faces with areas
$\{A_k\}_{k=1}^{N_A}$, normal vectors $\{\mathbf{n}_k\}_{k=1}^{N_A}$ and fluxes
$\{f_k\}_{k=1}^{N_A}$, a constant vector field $\mathbf{v}$ satisfying
\begin{equation*}
    \mathbf{v} = \argmin_{\mathbf{w}\in \mathbb{R}^3} \sum_{k=1}^{N_A}(A_k\mathbf{w} \cdot \mathbf{n}_k - f_k)^2.   
\end{equation*} can be computed through
\begin{equation*}
    \mathbf{v} = (\mathbb{K}^T\mathbb{K})^{-1}\mathbb{K}^T\mathbf{f},
\end{equation*}
where
\begin{equation*}
    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_{N_A}\mathbf{n}_{N_A}]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_{N_A}]^T,
\end{equation*}
and each vector in $\mathbb{R}^3$ is treated as a column vector. The construction based on
the integral quantities on edges can be done similarly. Assembling the local constructions
for each dual cell, the global construction can be written as
\begin{equation}
    \mathbf{E} = \Tilde{\mathbb{R}}_E\mathbf{d}\;,
    \quad
    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b},
    \label{equ:reconstruction}
\end{equation}
where $\mathbf{d}, \mathbf{b}$ are defined in Tab.~\ref{tab:def_size_var};
$\mathbf{E} := \{\mathbf{E}_k\}_{k=1}^{N_{\Tilde{V}}}$ and
$\mathbf{B} := \{\mathbf{B}_k\}_{k=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$
matrices containing the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each
$\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.

@@

3D FIT/DEC-FVM framework presented in Section~\ref{sec:spatial_discretization} and the
